Sound Automated Synthesis of Digital Controllers

### 2016-10-13 paper/paper.tex
revised sec 4.2

There are two approaches for the {\sc verify} phase based on the
described model.  The first uses interval arithmetic, representing the
coefficients
$[{c}_i-\Delta_p{c}_i-\Delta_b{c}_i\ ,\
{c}_i+\Delta_p{c}_i-\Delta_b{c}_i+(2^{-F_b})]$ 
and rounding operations outwards during the process. 
%\cdsay{dario, what coefficients are these?}
% This results in a
% tighter calculation of the error at the cost of
% performance.
Synthesised controllers using this verifier will always
be correct and only generate counterexamples when the precision of the
engine is insuficient.  Given the high computational cost of this
approach, we also designed a second approach, which we describe below.
In our implementation described in Sec.~\ref{sec:experiments}, we 
try both approaches and provide the time for the fastest. 
% show that the increase in speed of the second approach 
% over the first one is in most cases of several orders of magnitude.

In Fig.~\ref{fig:CEGIS}, we illustrate the second approach, which 
uses a two-stage verification. 
In the first stage, denoted by {\sc Uncertainty} in Fig.~\ref{fig:CEGIS}, 
assuming a certain precision \param{I_b}{F_b} for the uncertainty,
\cdsay{how about the controller?}
we check whether the system is unstable for the current candidate solution,
{\it i.e.}, if $\neg \phi_{stability}$ is satisfiable for $S(z)$.
If this is the case, then we obtain a counterexample 
$\Delta \vec{p}$, 
%denoted by values for each coefficients of $\Delta N_{G}(z)$ and $\Delta D_{G}(z)$, 
%\red{[see my comment above - these quantities pop up too abruptly.]},
which makes the closed-loop system unstable. 
This uncertainty is added to 
the set {\sc inputs} such that, in the subsequent {\sc synthesise} phase, 
we obtain a candidate solution consisting 
of a controller $D_C$ and $N_C$, which makes the closed-loop 
system stable for all the uncertainties accumulated in {\sc inputs}.

>>>>

There are two approaches for the {\sc verify} phase based on the
described model.  The first uses interval arithmetic 
\cdsay{Dario, can you please add a reference here?} to represent the
coefficients
$[{c}_i-\Delta_p{c}_i-\Delta_b{c}_i\ ,\
{c}_i+\Delta_p{c}_i-\Delta_b{c}_i+(2^{-F_b})]$ 
and the rounding operations outwards during the process. 
%\cdsay{dario, what coefficients are these?}
% This results in a
% tighter calculation of the error at the cost of
% performance.
Synthesised controllers using this verifier will always
be correct and only generate counterexamples when the precision of the
engine is insuficient.  Given the high computational cost of this
approach, we also designed a second approach, which we describe below.
Our experimental results described in Sec.~\ref{sec:experiments},  
%try both approaches and provide the time for the fastest. 
show that the increase in speed of the second approach 
over the first one is in most cases of several orders of magnitude.

In Fig.~\ref{fig:CEGIS}, we illustrate the second approach, which 
uses a two-stage verification such that in the first stage we 
assume a certain precision for the uncertainty
followed by a second stage, where we check the soundness of our assumption.

Essentially, in the first stage, denoted by {\sc Uncertainty} in Fig.~\ref{fig:CEGIS}, 
assuming a certain precision \param{I_b}{F_b} 
\cdsay{how about the controller?}
we check whether the system is unstable for the current candidate solution,
{\it i.e.}, if $\neg \phi_{stability}$ is satisfiable for $S(z)$.
If this is the case, then we obtain a counterexample 
$\Delta \vec{p}$, 
%denoted by values for each coefficients of $\Delta N_{G}(z)$ and $\Delta D_{G}(z)$, 
%\red{[see my comment above - these quantities pop up too abruptly.]},
which makes the closed-loop system unstable. 
This uncertainty is added to 
the set {\sc inputs} such that, in the subsequent {\sc synthesise} phase, 
we obtain a candidate solution consisting 
of a controller $D_C$ and $N_C$, which makes the closed-loop 
system stable for all the uncertainties accumulated in {\sc inputs}.
